IML Term project paper

### 2022-12-10 paper.rmd
Update paper.rmd
Korjattu mallinvalintaan liittyvä virhe support vector classifier-osiossa

For our model, we chose to run a 10-fold cross validation on a set of tuning parameters $C$ to assess which kernel performed best and chose to model the value based on that. In these preliminary assessments, we assessed the radial kernel had the best performance of the ones available in the R package e1071. For this kernel, we ran loo-cross validation to assess the value of tuning parameter $C$ and calculated for said tuning parameter loo-cross-validated accuracy and perplexity.

>>>>

For our model, we chose to run a 10-fold cross validation on a set of tuning parameters $C$ to assess which kernel performed best and chose to model the value based on that. In these preliminary assessments, we assessed the radial and linear kernels had the best performance of the ones available in the R package e1071. For these kernels, we ran loo-cross validation to assess the value of tuning parameter $C$ and calculated for said tuning parameter loo-cross-validated accuracy and perplexity. Eventually, the radial kernel had slightly better accuracy but the linear kernel had lower perplexity and as a result, we chose to use the linear kernel in our model
